RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-05-02 manuscripts/manuscript.Rmd
reorganizing into manuscripts

```{r compile-settings, include=FALSE}
library(knitr)
opts_chunk$set(tidy = FALSE, warning = FALSE, message = FALSE, 
               cache = 1, comment = NA, verbose = TRUE)
basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile') )
opts_chunk$set(fig.path = paste("figure/", basename, "-", sep=""),
               cache.path = paste("cache/", basename, "/", sep=""))

>>>>

```{r compile-settings, include=FALSE}
library(knitr)
opts_chunk$set(tidy = FALSE, warning = FALSE, message = FALSE, 
               cache = 1, comment = NA, verbose = TRUE)
basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile')) 
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))

### 2014-05-02 manuscripts/tutorial.Rmd
reorganizing into manuscripts

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```

@@

>>>>

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = imgur_upload)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```

@@

```{r include=FALSE}
unlink("example.xml")
unlink("meta_example.xml")
unlink("test.xml")
```
